\begin{abstract}

%Mapping across different platform or language Application Programming Interfaces (APIs)
%is highly desirable.
Developers often migrate applications to release different versions for supporting application programming interfaces (APIs) of various platforms/programming-languages.
To migrate an application written using one API (source) to another API (target), a developer needs to know
how the methods in the source API map to the methods in the target API.
Given a typical platform or language exposes a large number of API methods for developers to reuse,
manually writing these mappings is prohibitively resource-intensive
and may be error prone.
Recently, researchers proposed to automate the process by mining API mappings from existing code-bases.
However, these approaches require as input a manually ported (or at least functionally similar) code across source and target API's.
To address the shortcoming, this paper proposes \tool: \textit{\textbf{T}ext \textbf{M}ining
based approach to discover likely \textbf{AP}I mappings} using the 
similarity in the textual description of the source and target API documents.
To evaluate our approach, we apply \tool\ to discover API mappings for 15 classes across: 
1) \CodeIn{Java} and \CodeIn{C\#} API,
2) \CodeIn{Java ME} and \CodeIn{Android} API.
We next compare the discovered mappings with state-of-the-art source code analysis based approaches: Rosetta and StaMiner.
Our results indicate that \tool\ on an average found relevant mappings for 57\% more methods compared to previous approaches. 
Furthermore, our results also indicate that \tool\ found on average exact mappings for 6.5 more methods per class with a maximum of 21 additional exact mappings for a single class as compared to previous approaches.
\end{abstract}